### 2014-05-21 acks.tex
Final fixes and add -c helpers to acks

Many others helped to develop the ideas in this work, especially
Pratiksha Thaker, Chris Amato, Andrew McGregor, Tim Shepard, John
Wroclawski, Bill McCloskey, Josh Mandel, Carrie Niziolek, Damon
Wischik, Hariharan Rahul, Garrett Wollman, Juliusz Chroboczek, Chris
Lesniewski, Vikash Mansinghka, Eric Jonas, Marissa Cheng, and Allie
Brownell.

@@

>>>>

Many others helped to develop the ideas in this work, especially
Pratiksha Thaker, Chris Amato, Andrew McGregor, Tim Shepard, John
Wroclawski, Richard Barry, Bill McCloskey, Josh Mandel, Carrie Niziolek, Damon
Wischik, Hariharan Rahul, Garrett Wollman, Juliusz Chroboczek, Chris
Lesniewski, Vikash Mansinghka, Eric Jonas, Waseem Daher, Jeff Arnold, Marissa Cheng, and Allie
Brownell.

@@

Thank you to the subscribers of MIT Zephyr's help class, who
organized themselves at the last minute to proofread this
dissertation for me: Laura Baldwin, Jacob Morzinski, Mark Eichin, Carl
``Alex'' Alexander, Ben Kaduk, and Richard Tibbetts.

### 2014-05-21 learn_operational.tex
All fixes through 2:39 p.m.
Final fixes and add -c helpers to acks

Some congestion-control protocols have been designed for specific
kinds of networks~\cite{dctcp,westwood} or require explicit knowledge
of the link rate \emph{a priori}~\cite{xcp}. Others are intended as a
``one size fits all,'' including most variants of TCP.

@@

We investigated the consequences of designing a congestion-control
protocol with the knowledge that some cross-traffic may the product of
pre-existing incumbent protocols.

>>>>

Some congestion-control protocols have been designed for specific
kinds of networks~\cite{dctcp,westwood} or require explicit knowledge
of the link rate \emph{a priori}~\cite{xcp}. Others are intended as
one-size-fits-all solutions, including most variants of TCP.

@@

We investigated the consequences of designing a congestion-control
protocol with the knowledge that some cross-traffic may be the product of
pre-existing incumbent protocols.
